---
title: "Good Plot, Bad Plot"
author: "Nikolas Yousefi"
date: "3/15/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE,
                      message = FALSE)
```

# Libraries

```{r}
library(tidyverse)
library(here)
library(ggeasy)
library(extrafont)
library(ghibli)
library(viridis)
```

# Loading Data

```{r}
coffee_ratings <- read.csv(here("Week_7","Data","coffee_ratings.csv"))

glimpse(coffee_ratings)
```

# Analayzing Data

```{r}
coffee_clean <- coffee_ratings %>% 
  select(total_cup_points, species, country_of_origin) %>% #Selecting data of interest
  filter(species == "Arabica") %>% # Picking only Arabica beans 
  pivot_wider(names_from = species) %>% # Pivoting wider for easier analysis
  group_by(country_of_origin) %>% # Grouping to make getting mean easier
  summarise(mean_rating = mean(total_cup_points)) %>% # Getting mean of total cup points per country of origin
  drop_na() # Dropping any data with NAs
```

# Bad Plot

```{r, fig.width=10, fig.height=10}
ggplot(coffee_clean, aes(x=country_of_origin, y=mean_rating, fill = mean_rating, color = country_of_origin))+ # Setting up initial graph
  geom_bar(stat="identity")+ # Setting up as a bar graph
  theme_minimal() + # Minimal theme
  ylim(-50,100)+ # y-limit for making circular bar graph 
  theme(text = element_text(family = "Jokerman",
                            face = "bold"), # Selecting font and bolding
    plot.background = element_rect(fill = ghibli_palette("TotoroDark")[c(2)]), # Filling background with a specific color
    plot.title = element_text(colour = ghibli_palette("MononokeMedium")[c(2)], size = 30), # Labeling plot title with a specific color
    plot.caption = element_text(size = 18), # Plot caption size
    legend.title = element_text(size = 25,
                                family = "Chiller"), # Legend title size and font type
    axis.text = element_blank(), # No axes text
    axis.title = element_blank(), # No axes titles
    panel.grid = element_blank())+ # No grid
coord_polar(start = 0)+ # Turning cartesian graph into a circular one
scale_fill_gradient(low = "#6F4E37", high = "#7B3F00")+ # Setting legend gradient
geom_text(data=coffee_clean,
          aes(x=country_of_origin,
              y=mean_rating,
              label=country_of_origin,
              hjust= 0.5,
              vjust = -0.5),
          family = "Vivaldi")+ # Setting up the circular bar plot font and adjusting text location
  labs(title = "coffee analysis",
       caption = "WHO WANTS CAWFEE?! - Vic Dibitetto")+ # Adding title and caption
  ggsave(here("Week_7", "Output", "badplot.png"),
         width = 10, height = 10) # Saving in specified area and at specific size
           
```

## Why this plot is bad

-   Generic title that does not convey what the actual analysis is about

-   Title also lacks proper capitalization

-   Dark text against a dark background makes many of the words hard to read and is definitely not color-blind friendly

-   Circular bar graph makes the data hard to interpret, especially with the lack of axes to determine what is being analyzed

-   Multicolored text denoting the countries on the bar graph overlaps against one another and is not a standard font, making it near illegible

-   Using a gradient to specify the means, especially one where the "low" and "high" colors are very similar, makes it hard to parse the data ; much of the data are also not whole numbers

-   Useless legend denoting country of origin that not only uses a gradient style, making it hard to read, but also bleeds out of the graph

-   Both legends also lack proper titles, instead opting for the ones directly used in the raw data

-   Three different, non-standard font styles are used in the graph, legend, title, and caption

-   The caption, which is usually meant to specify the source from which this data comes from, is replaced with a funny, but useless quote

# Good Plot

```{r, fig.width = 9, fig.height = 7}
coffeegood <- coffee_clean %>% 
  filter(mean_rating >= 82.8300) # Filtering so only top 10 are included

ggplot(coffeegood, aes(x=country_of_origin, y=mean_rating, fill = country_of_origin))+ # Setting up the graph
  geom_bar(stat = "identity", show.legend = FALSE)+ # Using a bar graph for these data
  theme_bw()+ # Selecting a basic theme
  coord_flip()+ # Flipping axes
  scale_fill_viridis_d()+ # Going with a color-blind friendly color for the bars
  theme(plot.title = element_text(size = 16), # Changing title size
        axis.text = element_text(size = 12), # Changing text size of the axes text
        axis.title.x = element_text(size = 14), # Changing axis text size
        axis.title.y = element_text(size = 14))+ # Changing axis text size)
labs(x = "Country of Origin",
       y = "Average Cup Points",
       title = "Average Cup Points of Arabica Coffee for Top Ten Countries",
       caption = "Source: rfordatascience/tidytuesday and Coffee Quality Database")+ # Adding axes titles, as well as a graph title and caption
  ggeasy::easy_center_title()+ # Centering title
    ggsave(here("Week_7", "Output", "goodplot.png"),
         width = 9, height = 7) # Saving in specified area and at specific size
```

## Why this plot is good

-   No vibrant-colored backgrounds or text making words or data hard to read or interpret

-   While optional, the data has been cleaned and reduced so 30+ different countries of origin aren't being graphed

-   Title accurately states what the plot is looking to measure and visualize

-   Axes are properly labeled

-   Text is large, readable, and without distracting font types

-   Bar graph colors are color-blind friendly

-   No unnecessary legends

-   Caption properly cites where the data was originally sourced from
